Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-04-28 cikm2016/cikm_dateparse.tex
CIKM formatting
Some rewording in the abstract and removal of orphan words.

%\documentclass{acm_proc_article-sp}
\documentclass[conference]{IEEEtran}
%
\usepackage{url}
\usepackage{syntax}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\usepackage{mathtools}
\usepackage{color}
\usepackage{caption} 
\usepackage{tikz}
\captionsetup[table]{skip=10pt}

\def\eg{\textit{e.g.} }
\def\ie{\textit{i.e.} }
\def\dateparse{\mbox{\texttt{DATEPARSE}}}
\hyphenation{time-stamp}

@@

\title{Does Anybody Really Know What Time It Is?\\
Automating the Extraction of Date Scalars}
\input{authors}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Michael Shell}
%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: http://www.michaelshell.org/contact.html}
%\and
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%}}

\maketitle
\begin{abstract}
Interactive visual analytics is an effective approach for the timely analysis of big data. Users who are already engaged in interactive data analysis prefer to stay in the visualization environment for unavoidable cleaning and preparation tasks in order to preserve their analytic flow. This has led visualization environments to include simple data preparation functions such as scalar parsing, pattern matching and categorical binning in their analytic toolkits. One of the most common scalar parsing tasks is extracting date and time data from string representations. Several RDBMSes include date parsing ``mini-languages'' to cover the wide range of possible formats, but analysis of user data from one visualization system shows that the parsing language syntax is difficult for users to master without disturbing their analytic flow.

In this paper, we present two algorithms for automatically deriving these date formats from a column of data with minimal user disruption, one based on minimal entropy representations and another based on natural language processing techniques. Both have accuracies of over 95\% on a large corpus of date columns extracted from an online data repository and are in substantial agreement with each other. One approach is also fast enough to produce results within the user's perceptual threshold, making it suitable for interactive work.
\end{abstract}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
\input{acknowledgements}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\IEEEtriggeratref{24}
\bibliographystyle{IEEEtran}
\bibliography{dateparse}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ``.bib'' file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%

>>>>

%\documentclass{acm_proc_article-sp}
%\documentclass[conference]{IEEEtran}
\documentclass{sig-alternate-05-2015}
%
\usepackage{url}
\usepackage{syntax}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\usepackage{mathtools}
\usepackage{color}
\usepackage{caption} 
\usepackage{tikz}
\captionsetup[table]{skip=10pt}

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
\def\eg{\textit{e.g.} }
\def\ie{\textit{i.e.} }
\def\dateparse{\mbox{\texttt{DATEPARSE}}}
\hyphenation{time-stamp}

@@

\title{Does Anybody Really Know What Time It Is?\\
Automating the Extraction of Date Scalars}
\input{anonymous}

\maketitle
\begin{abstract}
Interactive visual analytics is an effective approach for the timely analysis of big data. Users who are already engaged in interactive data analysis prefer to stay in the visualization environment for unavoidable data cleaning and preparation tasks in order to preserve their analytic flow. This has led visualization environments to include simple data preparation functions such as scalar parsing, pattern matching and categorical binning. One of the most common scalar parsing tasks is extracting date and time data from string representations. Several relational database systems include date parsing ``mini-languages'' to cover the wide range of possible formats, but analysis of user data from one visualization system shows that the parsing language syntax is difficult for users to master without disturbing their analytic flow.

In this paper, we present two algorithms for automatically deriving date formats from a column of data with minimal user disruption, one based on minimal entropy representations and another based on natural language processing techniques. Both have accuracies of over 95\% on a large corpus of date columns extracted from an online data repository and are in substantial agreement with each other. One approach is also fast enough to produce results within the user's perceptual threshold, making it suitable for interactive work.
\end{abstract}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
\input{credits}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{dateparse}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ``.bib'' file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
